Learning complex models with invertible neural networks: a likelihood-free Bayesian approach

### 2019-06-23 latex/paper_main.tex
Compute all metrices

\begin{figure}
    \centering
    \subfloat[Training phase]{{\includegraphics[width=.99\linewidth]{training.png}}}
    \newline
    \subfloat[Inference phase]{{\includegraphics[width=.99\linewidth]{inference.png}}}
    \caption{A graphic illustration of the two phases of the method. \textbf{(a)} During the training phase, the networks are trained on simulated data from the model; \textbf{(b)} during the inference phase, the posterior is approximated from real data.}
    \label{fig:first}
\end{figure}

>>>>

\begin{figure}
    \centering
    \subfloat[Training phase]{{\includegraphics[width=.99\linewidth]{training.png}}}
    \newline
    \subfloat[Inference phase]{{\includegraphics[width=.99\linewidth]{inference.png}}}
    \caption{A graphic illustration of the two phases of the method. \textbf{(a)} During the training phase, the networks are trained on simulated data from the model; \textbf{(b)} during the inference phase, the true posterior of the model parameters is approximated from real data.}
    \label{fig:first}
\end{figure}
